Full-depth Coadds of the WISE and First-year NEOWISE-Reactivation Images

### 2016-02-29 ms.tex
added quadrant warp example figure

% figure showing single-tile example of removed moon contamination

@@

Figure 3 provides an illustration of our polynomial background modeling
procedure. We were able to recover 54\% of Moon-contaminated data
in W1 and 33\% in W2. We also apply this polynomial
correction procedure to frames that we flagged as potentially affected
by scattered light halos from bright solar system planets.

@@

@@

Figure 6 shows zoom-ins of low ecliptic latitude fields which illustrate
visually the reduction in statistical noise which has been achieved
by doubling the number of input exposures.

@@

% figure showing before/after of SGP on large scales in both W1/W2
% figure showing close-up at low ecl latitude with reduced noise

% would be fun to say how many pixels of output there are total

>>>>

@@

Figure \ref{fig:warp_example} provides an illustration of our polynomial 
background modeling procedure. We were able to recover 54\% of 
Moon-contaminated data in W1 and 33\% in W2. We also apply this polynomial
correction procedure to frames that we flagged as potentially affected
by scattered light halos from bright solar system planets.

@@

\begin{figure*}
 \begin{center}
  \epsfig{file=05245b140_w1_q2.eps, width=7.0in}
  \caption{\label{fig:warp_example} Illustration of the procedure by which
           we recover Moon-contaminated exposures, as described in 
           $\S$\ref{sec:recover}. Shown here is quadrant 2
           of W1 exposure 05245b140. This quadrant was successfully recovered.}
% mention which tile used as reference?
 \end{center}
\end{figure*}

@@

Figure \ref{fig:image_noise} shows zoom-ins of low ecliptic latitude fields 
which illustrate visually the reduction in statistical noise which has been 
achieved by doubling the number of input exposures.

% figure showing close-up at low ecl latitude with reduced noise

@@

% figure showing before/after of SGP on large scales in both W1/W2
